Primes Paper

### 2013-09-02 Primes Write up.tex

\documentclass[12pt, Helvetica]{article}   	
\title{Primes Paper}
\author{Nick Kaashoek and William Wu}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCS, also known as massive open online courses, leading to a rise in their importance for educating students around the world as well as a tremendous amount of funding for these courses. Both the MOOCS systems coursera and edX; 370,000 in edX and 1.7 million in coursera, these enormous numbers show that MOOCS are extremely important to the education system. The amount of money poured into them also reveals this, with 60 million dollars put into edX. The huge number of students in these courses also lead to a very high student to professor ratio, 150,000:1 in some courses.

The increase in the number of students assigned to a single proffesor in such courses leads to many problems, not the least of which is the inability of a single professor to grade all the assignments they give out, which can sometimes number in the thousands. To solve this problem, there are two man solutions in use today; automated grading and peer grading. Automated grading relys on having machines grade papers; this is fast, but it may not always be fair to students because machines can only handle a certain number of answers, limiting the types of questions that may be asked. Peer grading, however, has no limit on grading, but a system utilizing it could be "hacked" by the students. In practice, though, both of these systems are unpolished and rather inefficient.

The problem that we have located is important to solve, because without it the MOOCS cannot provide efficient feedback for their students. Without his feedback, students are unable to effectively evaluate what they know and do not know, limiting their learning abilities. As such, it is imperitive that an efficient system is created to allow these students to learn and grow efficiently. This is our goal.

With the importance of such a problem, there have been many attempts at solving it; however all these attempts lack one thing, which we hope to introduce into our solution. In all previous attempts and current designs for grading the papers of students, there is something lacking; a rigourous mathematical proof and analysis of the system. With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions. Introducing this to the problem will help to create a concrete system of grading that will consistently and universally produce positive results, both in terms of efficiency, and fairness for the students.

@@

Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve
\end{document}

>>>>

\documentclass[12pt, Helvetica]{article}   	
\title{Primes Paper}
\author{Nick Kaashoek and William Wu}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars\cite{canmoocsreducecc}. However, the MOOC's main importance comes from it's scalability. Moocs are able to educate massive numbers of students from anywhere in the world\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem. Currently, there are two ways to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers, severly limiting the depth of the questions asked\cite{rightandwrongmoocs}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students \cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.

The problem that we have located is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge. Because this limits their learning abilities, it is imperitive to create an efficient system that enables students to learn efficiently and grow. This is our goal.

There have been many attempts at solving such an important problem. However, we hope to introduce what all previous attempts lack: a rigourous mathematical proof and analysis of the system. With our system, we hope to introduce a set of criteria that the system must pass, and then analyze it mathematically to prove the efficiency of our solutions. Introducing this to the problem will help to create a concrete system of grading that will consistently and universally produce positive results, both in terms of efficiency, and fairness for the students.

@@

Although this is not as good as our previous mechanism, it is still an improvement because there is now positive competition instead of negaitve

\begin{thebibliography}

\bibitem{canmoocsreducecc}
  http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
  Author,
  \emph{Title}.
  Source,
  Year.
  Ruth, S. (2012). Can MOOCís and existing e-learning paradigms help reduce college costs? International Journal of Technology in Teaching and Learning, 8(1), 21-32.

\bibitem{makingsenseofmoocs}
  http://www-jime.open.ac.uk/jime/article/viewArticle/2012-18/html
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{swotanalysisofmoocs}
  http://www.editlib.org/p/112020
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{rightandwrongmoocs}
  http://www.tonybates.ca/2012/08/05/whats-right-and-whats-wrong-about-coursera-style-moocs/
  Author,
  \emph{Title}.
  Source,
  Year.

\bibitem{test}
  Author,
  \emph{Title}.
  Source,
  Year.

\end{thebibliography}
\end{document}
